Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-03-26 paper.tex
Make some minor changes to Figure calls to be consistent with AMS guidelines.
Correct typos.

\cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
Although the warm anomaly in their simulation maximized in the mid-levels, they noted that a secondary warming maximum also existed in the 12-14-km layer.
Radial and vertical advection both played important roles in this warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
The warming of the upper troposophere by these advective and diffusive processes could decrease the vertical $\theta$ gradient, thereby contributing to a decrease in static stability near the tropoopause within the eye.

@@

In the tropopause layer, some of the budget terms are small enough to be ignored.
To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq. \ref{eq:dthetadt} to the tropopause-layer static stability tendency is plotted in Fig.~\ref{fig:avgbudterms}.
For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
The absolute values of these tendencies are then averaged over the radius-height domain of the plots shown in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain. 
Thus, taking an average over the domain tends to wash out the positive and negative contributions.
To circumvent this problem, the absolute value of each of the terms is averaged.}. 
Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
The remaining three processes - horizontal turbulence, microphysics, and dissipative heating -  are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.

@@

%The eye was characterized by stabilization below 16 km and destabilization in the 16-17-km and 18-19-km layers.
%Comparing Fig.~\ref{fig:stab-24-48}b to \ref{fig:adv-24-48}a,b reveals that the stabilization below 16 km in the eye was forced by vertical advection, as was the region of destabilization in the 18-19-km layer.
%Meanwhile, the destabilization that occurred in the 16-17-km layer was forced by a combination and radial and vertial advection.

@@

%In this region of mean ascent, changes in the vertical gradint of mean vertical velocity are responsible for alternating regions of positive and negative $N^2$ tendencies.

@@

%Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acted within the outflow jet.
%For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
%Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
%This switch in signs was a consequence of a reversal of the radial graident of mean $N^2$ near the 140-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
%Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq. \ref{eq:advtend}; outside of that radius $(\partial/\partial r)(\partial \theta/\partial z) < 0$ and $u > 0$, which corresponds to forcing for stabilization.
%
%The relative imporance of the first and third terms on the right-hand side of Eq. \ref{eq:advtend} is difficult to ascertain, but the structure of the mean radial velocity, $\theta$, and $N^2$ fields suggests that both terms are contributing within the outflow layer.

@@

%FIGURE 2%
\begin{figure}[ht]
\centerline{\includegraphics[width=39pc]{mod+bud+res.png}}
\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange} over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).
Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:mod+bud+res}
\end{figure}

@@

%FIGURE 9%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{qi+radten.png}}
\end{figure*}
\begin{figure}
\caption{Ice mixing ratio (g kg\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (c) 24-48 hours, and (e) 48-72 hours. Radiative heating rate (K h\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (b) 0-24 hours, (d) 24-48 hours, and (f) 48-72 hours.} 
\label{fig:qi+radten}
\end{figure}

@@

%FIGURE 11%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{khvten.png}}
\caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold-point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
\label{fig:diff}
\end{figure*}

%FIGURE 12%
\begin{figure*}[ht]
\centerline{\includegraphics[width=19pc]{fulltrop.png}}
\end{figure*}
\begin{figure}
\caption{(Top panel) Change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) directly output by the model for the 0-21-km layer. (Middle panel) Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}) averaged over the same time period. (Bottom panel) Radiative heating rate (K h\textsuperscript{-1}) averaged over the same time period.}
\label{fig:fulltrop}
\end{figure}

>>>>

\cite{SternZhang2013} described the development of the TC warm core using a potential temperature ($\theta$) budget analysis.
Although the warm anomaly in their simulation maximized in the mid-levels, they noted that a secondary warming maximum also existed in the 12-14-km layer.
Radial and vertical advection both played important roles in this warm core development throughout RI, and subgrid-scale diffusion became particularly important during the later stage of RI.
The warming of the upper troposphere by these advective and diffusive processes could decrease the vertical $\theta$ gradient, thereby contributing to a decrease in static stability near the tropopause within the eye.

@@

In the tropopause layer, some of the budget terms are small enough to be ignored.
To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq. \ref{eq:dthetadt} to the tropopause-layer static stability tendency is plotted in Fig.~\ref{fig:avgbudterms}.
For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
The absolute values of these tendencies are then averaged over the radius-height domain of the plots shown in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain. 
Thus, taking an average over the domain tends to wash out the positive and negative contributions.
To circumvent this problem, the absolute value of each of the terms is averaged.}. 
Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
The remaining three processes - horizontal turbulence, microphysics, and dissipative heating -  are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.

@@

%The eye was characterized by stabilization below 16 km and destabilization in the 16-17-km and 18-19-km layers.
%Comparing Fig.~\ref{fig:stab-24-48}b to \ref{fig:adv-24-48}a,b reveals that the stabilization below 16 km in the eye was forced by vertical advection, as was the region of destabilization in the 18-19-km layer.
%Meanwhile, the destabilization that occurred in the 16-17-km layer was forced by a combination and radial and vertical advection.

@@

%In this region of mean ascent, changes in the vertical gradient of mean vertical velocity are responsible for alternating regions of positive and negative $N^2$ tendencies.

@@

%Advection of $N^2$ by the radial wind (first term on the right-hand side of Eq. \ref{eq:advtend}) also acted within the outflow jet.
%For example, horizontal advection provided forcing for destabilization at the 16-km level almost everywhere inside of the 140-km radius.
%Outside of this radius near 16 km, however, existed a region of forcing for stabilization.
%This switch in signs was a consequence of a reversal of the radial gradient of mean $N^2$ near the 140-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
%Inside of that radius, $(\partial/\partial r)(\partial \theta/\partial z) > 0$ and $u > 0$, which corresponds to forcing for destabilization in Eq. \ref{eq:advtend}; outside of that radius $(\partial/\partial r)(\partial \theta/\partial z) < 0$ and $u > 0$, which corresponds to forcing for stabilization.
%
%The relative importance of the first and third terms on the right-hand side of Eq. \ref{eq:advtend} is difficult to ascertain, but the structure of the mean radial velocity, $\theta$, and $N^2$ fields suggests that both terms are contributing within the outflow layer.

@@

%FIGURE 2%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{mod+bud+res.png}}
\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange} over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).
Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:mod+bud+res}
\end{figure*}

@@

%FIGURE 9%
\begin{figure}[ht]
\centerline{\includegraphics[width=39pc]{qi+radten.png}}
\end{figure}
\begin{figure}
\caption{Ice mixing ratio (g kg\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (a) 0-24 hours, (c) 24-48 hours, and (e) 48-72 hours. Radiative heating rate (K h\textsuperscript{-1}) and cold-point tropopause height (orange lines) averaged over (b) 0-24 hours, (d) 24-48 hours, and (f) 48-72 hours.} 
\label{fig:qi+radten}
\end{figure}

@@

%FIGURE 11%
\begin{figure}[ht]
\centerline{\includegraphics[width=39pc]{khvten.png}}
\caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold-point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
\label{fig:diff}
\end{figure}

%FIGURE 12%
\begin{figure}[ht]
\centerline{\includegraphics[width=19pc]{fulltrop.png}}
\end{figure}
\begin{figure}
\caption{(Top panel) Change in $N^2$ over the 24-48-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) directly output by the model for the 0-21-km layer. (Middle panel) Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}) averaged over the same time period. (Bottom panel) Radiative heating rate (K h\textsuperscript{-1}) averaged over the same time period.}
\label{fig:fulltrop}
\end{figure}
